Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex
iniciamos la redacción de las conclusiones con un resumen de lo que se ha presentado y lo que se ha obtenido en los experimentos

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a GET function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions.

@@

The conclusion goes here.

>>>>

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a GET function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, Table \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions.

@@

% The conclusion goes here.

In this paper a client-server architecture for distributed evolutionary algorithms, termed {\sf NodIO}, for volunteer computing has been presented.

In order to establish a baseline performance, the evolutionary algorithm was run in a desktop client-program written in JavaScript using NodEO to solve the 40-trap function.
In this first experiment, it could be observed how many users donated a few cycles and just a few donated a high amount of CPU to the experiment.

As a second experiment, and trying to improve the number of cycles per user, the system architecture was modified. In this case, Web Workers were used so that several clients per browers could be executed.
As a result, in this case a higher number of contributions per volunteer could be observed, although as in the previous experiments a pattern of a few users with many contributions and many with few contributions was obtained.
